RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-27 main.tex
:pencil: Add remark on SIC

	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based cooperative networks.

@@

		One special property of scatter-based cooperative networks is the backscatter signal strength is significantly weaker than primary due to the double fading effect.

@@

		However, the assumption of very large backscatter-over-primary symbol period ratio may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.

@@

		Besides, all relevant literatures considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.

@@

		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based cooperative networks.
		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath in the primary equivalent channel as dynamic passive beamforming at each backscatter block.
		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load switching speeds.

@@

		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
		RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.
		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.85\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Time Structure]{
				\resizebox{0.9\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.

		\begin{remark}
			Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC). For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel (4). To accommodate such signal characteristics, novel receiving strategy apart from SIC is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
		\end{remark}
		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
			}
			\label{fg:energy_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
	\end{subsection}

>>>>

	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed receiver significantly reduces the decoding complexity and effectively accommodates the double modulation and signal difference in scatter-based multiple access.

@@

		One special property of scatter-based multiple access is the backscatter signal strength is significantly weaker than primary due to the double fading effect.

@@

		However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice \footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.

@@

		Besides, all relevant literatures consider either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} for backscatter information sources.

@@

		\emph{Second,} we propose a practical receiver that accommodates the double modulation and signal difference in scatter-based multiple access.
		Since the primary and backscatter messages are superimposed by multiplication coding and the backscatter symbol is typically longer than primary, the scattered signals from RIScatter nodes can be treated as multipath components during primary decoding, and the primary message can be viewed as a spreading code during backscatter decoding.
		Conventional sequential primary-backscatter decoder eliminates primary interference by \gls{sic} at each primary block, while our sequential backscatter-primary detector semi-coherently decodes RIScatter nodes from the received energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath in the primary equivalent channel as dynamic passive beamforming at each backscatter block.
		It enables backscatter modulation and dynamic passive beamforming at much lower operational complexity, and is suitable for scatter nodes with various load switching speeds.

@@

		As a generalization of \gls{bc}, \gls{sr} and \gls{ris}, RIScatter is a passive scattering protocol that cooperatives with an active primary link in a flexible and mutualistic manner.
		RIScatter nodes utilizes \gls{csi}- and weight-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.85\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Time Structure]{
				\resizebox{0.9\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and time structure of \gls{bc}, \gls{ambc}, \gls{sr}, \gls{ris}, and RIScatter.
				``PB'' means primary block and ``BB'' means backscatter block.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		% The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		% Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		% Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		% Besides, joint encoding over multiple co-located RIScatter nodes can further improve the total backscatter rate.

		\begin{remark}
			Scatter-based multiple access involves a double modulation where the primary and backscatter symbols of different length are superimposed by multiplication coding.
			The reflection pattern not only encodes the backscatter message, but also affects the primary equivalent channel.
			% Hence, \gls{sic}, which was originally proposed for superposition coding,
			It suggests backscatter detection under primary uncertainty can be viewed as part of primary channel training, and novel decoding strategies apart from \gls{sic}
			\footnote{
				Recall that \gls{sic} was proposed to achieve the capacity vertices for \gls{mac} with superposition coding.
				For scatter-based multiple access, \gls{sic} not only fails to exploit the double modulation effect, but also requires $N$ re-encoding, precoding and subtraction steps with a time-domain \gls{mrc} during each backscatter symbol block.
			}
			is desired to fully exploit signal characteristics and improve the primary-backscatter tradeoff.

			% Since scatter nodes directly modulate their message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
			% Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
			% Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.

			% Metascatter involves a symbiotic MAC where the primary and backscatter symbols of different duration are mixed by Multiplication Coding (MC) instead of Superposition Coding (SC). For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel (4). To accommodate such signal characteristics, novel receiving strategy apart from SIC is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
		\end{remark}
		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
			}
			\label{fg:energy_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fg:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
	\end{subsection}
